---
title: "Gov 50 Final Project"
author: "Tasia Avery"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Introduction

Introduction:
Across the world there is a problem with corruption. Corruption impacts several people as it can lead to loss of wealth, loss of life, and other serious consequences. According to a study by the United Nations Office on Drugs and Crime (UNODC) corruption most severely impacts vulnerable populations. Vulnerable populations can be identified as women, children, prisoners, those with mental health disorders, etc. As individuals across the world are impacted by corruption, it is important to identify which steps can be taken to reduce this human phenomena, and help the vulnerable individuals most greatly impacted. Given that vulnerable populations are more greatly effected, it is important that they have a voice in the government in order to ensure they are heard. Unfortunately, women and children are greatly under-represented in governments globally, and as such their voices are not heard. Nonetheless, there ARE women who hold political office, and political power, it is merely at a much lower rate than their male counterparts. Given that women are more likely to be affected by corruption than men, does that imply a decrease in corruption when women are more involved in the government?

One governmental role women serve in is holding the office of Diplomat. A diplomat is someone that is sanctioned by a government or instiution such as the United Nations to conduct diplomacy with foreign countries. Because it is easy to track the number of diplomats due to international relations, this will be the variable we use. I hypothesize, that countries that both send and receive more female diplomats will be perceived as less corrupt by their citizens. I believe this because a country with a higher quality of life typically has a lower rate of corruption, and equality is associated with that higher quality of life. I expect to see countries with higher perceived corruption to have less female diplomats overall. This finding could be significant to countries as if true, it would indicate that by involving more females in government (therefore hearing more ideas and perspectives) they could decrease their perceived corruption. 

## Data:
My data comes from two different sources. The first piece of data was collected from Transparency International. This takes the Corruption Perception Index, and analyzes 180 different countries. Countries with values closer to 0 are highly corrupt, where as countries with scores closer to 100 are less corrupt. The other portion of my data comes from a dataset produced by the University of Gothenburg, that compiles data regarding the gender and role of diplomats in international relations. It can be important to study the gender of diplomats in regards to corruption, as it can allow us to understand if women’s involvement in diplomacy has any impact on perceived corruption. 

Given that the corruption perception data was already nicely separated into 5 regions, I first ran an analysis on that producing a graph of the perceived corruption of each country in each region, finding that Africa has the highest level of perceived corruption, and countries in Western Europe have the least. Knowing this information, I decided to compare the amount of diplomats in each country. 

Region Values for Corruption:
1 - Africa
2 - Asia and Pacific Islands
3 - Eastern European 
4 - Latin America and Carribean
5 - Western European and other 

Region Values for Gender:
0 - Africa
1 - Asia 
2 - Central and North America
3 - Europe
4 - Middle East
5 - Nordic Countries
6 - Oceania 
7 - South America

```{r}
library(tidyverse)
library(ggplot2)
library(readxl)
corrdata <- read_excel("~/Downloads/Corruptclean2 (1).xlsx")
corrdata <- na.omit(corrdata)
genderdata <- read_excel("GenDip_Dataset_1968-2021.xlsx")

corrdata <- corrdata |>
  mutate(
    year = as.integer(year), 
      corrupt_perc = as.integer(corrupt_perc)
  )


genderdata <- genderdata |>
  mutate(
    gender = if_else(gender == 1, "Female", "Male")
  ) 

africacorrdata <- corrdata |>
  filter(region == "1")
corrdata 
## only corruption data for African countries

toafrica_genderdata <- genderdata |>
  filter(region_receive == "0" | cname_receive == "Algeria" )


toafrica_genderdata <- toafrica_genderdata |> 
  filter(year == "2003" | year == "2008" | year == "2013" | year == "2014")
toafrica_genderdata


fromafrica_genderdata <- genderdata |>
  filter(region_send == "0" | cname_send == "Algeria")


fromafrica_genderdata <- fromafrica_genderdata |> 
  filter(year == "2003" | year == "2008" | year == "2013" | year == "2014")
fromafrica_genderdata

toafrica_genderdata <- toafrica_genderdata |>
  select(year, cname_receive, gender, region_send)

fromafrica_genderdata <- fromafrica_genderdata |>
  select(year, cname_send, gender, region_receive)

toafrica_genderdata <- toafrica_genderdata |>
  group_by(year, cname_receive, region_send) |>
  count(gender) |>
   rename(diplomats_received = n,
          country = cname_receive)

fromafrica_genderdata <- fromafrica_genderdata |>
  group_by(year, cname_send, region_receive) |>
  count(gender) |>
   rename(diplomats_sent = n,
          country = cname_send)

jointdata <- africacorrdata |>
  left_join(toafrica_genderdata, by = join_by(country, year)) |>
  rename(to_africa_gender = gender)


jointdata <- jointdata |>
  left_join(fromafrica_genderdata, by = join_by(country, year)) |>
  rename(from_africa_gender = gender)
```

The graph below shows the average corruption in African countries from 2000-2015. Corruption is the the dependent variable in this study, and further research is going to be used to determine whether or not female diplomats contribute to lower levels of corruption. 

```{r}
africancorruption <- ggplot(data = jointdata,
                  mapping = aes(x = year, y = corrupt_perc)) +
  geom_line(mapping = aes(group = country), color = "gray70") + 
  geom_smooth(method = "loess", se = FALSE, linewidth = 1.1, color = "blue") +
  labs(
                x = "Year",
                y = "Corruption Level",
                title = "Corruption in Africa 2000-2015 Plot"
              )
africancorruption
```

To begin, I looked at the 10 most corrupt, and 10 least corrupt countries in Africa so that I could better analyze the differences in diplomats given their regional similarity. 

```{r}
jointdata <- jointdata |>
  group_by(country) |>
  mutate(avg_corruption = mean(corrupt_perc, na.rm = TRUE))

least_corrupt_summary <- jointdata |> 
  group_by(country) |>
  summarize(avg_corruption = mean(corrupt_perc, na.rm = TRUE)) |>
  slice_max(avg_corruption, n = 10)
least_corrupt_summary

most_corrupt_summary <- jointdata |> 
  group_by(country) |>
  summarize(avg_corruption = mean(corrupt_perc, na.rm = TRUE)) |>
  slice_min(avg_corruption, n = 10)
most_corrupt_summary

jointdata <- jointdata |>
  mutate(
    corruption_group = case_when(
      avg_corruption < 20.34 ~ "10 Most Corrupt",
      avg_corruption >= 20.34 & avg_corruption < 42.609 ~ "In the Middle",
      avg_corruption >= 42.609 ~ "10 Least Corrupt"
    )
  )
least_corrupt_summary2 <- jointdata |> 
  group_by(country) |>
  summarize(avg_corruption = mean(corrupt_perc, na.rm = TRUE)) |>
  slice_max(avg_corruption, n = 10) |>
  ggplot(mapping = aes(y = fct_reorder(country, avg_corruption),
                      x = avg_corruption)) +
  geom_col() + 
  labs(
    x = "Average Perceived Corruption", 
    y = "Country",
    title = "10 Least Corrupt Countries in Africa"
  )
least_corrupt_summary2

most_corrupt_summary2 <- jointdata |> 
  group_by(country) |>
  summarize(avg_corruption = mean(corrupt_perc, na.rm = TRUE)) |> 
  slice_min(avg_corruption, n = 10) |>
  ggplot(mapping = aes(y = fct_reorder(country, avg_corruption),
                      x = avg_corruption)) +
  geom_col() + 
  labs(
    x = "Average Perceived Corruption", 
    y = "Country",
    title = "10 Most Corrupt Countries in Africa"
  )
most_corrupt_summary2
```

```{r}
corr_jointdata <- jointdata |> 
  filter(corruption_group == "10 Most Corrupt" | corruption_group == "10 Least Corrupt")
  
corr_jointdata <- corr_jointdata |>
  group_by(country) |>
  mutate(total_dips_sent = sum(diplomats_sent, na.rm = TRUE))

fromgender_count <- fromafrica_genderdata |>
  count(gender)
fromgender_count

receivinggenderdata_table <- fromafrica_genderdata |>
  group_by(gender, region_receive) |>
  summarize(n = n())
knitr::kable(receivinggenderdata_table)
```
Africa sent 3 times the amount of male diplomats compared to female diplomats 


## Results
The results from my study are unfortunately inconclusive. I have reformatted my data several different times, and have been unable to come to a logical solution. However, it would seem that there is little correlation, but it could be due to lack of data, and a very poor analysis. 

## Citations
Niklasson, Birgitta and Ann E. Towns. 2023. The GenDip Dataset on Gender and Diplomatic
Representation, version June23. University of Gothenburg: The GenDip Program:
www.gu.se/en/gendip/gendip-data


Transparency International. 2022. 2022 Corruption Perception Index Report






















