---
title: "Gov 50 Final Project"
author: "Tasia Avery"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

I am interested in exploring data related to political culture. I am not 100% sure what I want to evaluate yet, but I think that analyzing the connection within a political context is something I am most interested in. 


For my final project I will be analyzing data related to political culture, and political environment. It is very important to compare different countries across a span of years in order to gain better information as to how they have changed over time individually, but also in comparison to other countries. I have currently sourced data from transparency international, that details the perception of government corruption in various countries across the globe from 2000-2015. 

The question I would like to answer in my research, is what forms of government across the globe have the highest perception of government corruption (and is the a correlation). I would also like to find data on womens involvement in governments over the same time span, and analyze the impacts of that alongside what forms of government are most open to women. 

The data I have begun to collect for this analysis is very large. There are over 3000 rows in the data frame that i have currently rewritten to match the code, as such, there is more data being added to this analysis, and limitations on available data may change the overarching analysis. However, despite this, I believe that it is important to analyze these countries in terms of the regions they are a part of, as well as analyzing similar traits among countries whenever possible. As the world moves forward it is important that governments are open and honest, but also representative of the people and ideas that they govern. For that reason, I believe that it is important to analyze the different types of governments that countries use to govern, but also the involvement of women who are representative of approximately half of the world's population. 

[Important note about current dataset] The data has recently been reformatted, and as such the corrupt_perc variable is currently not formatted correctly. The data is correct, but the scale on the y axis will be 0-100. Values closer to 100 are representative of a country with lower levels of corruption (they have a more honest government), and values closer to 0 represent a very corrupt government.

Region Values:
1 - Africa
2 - Asia and Pacific Islands
3 - Eastern European 
4 - Latin America and Carribean
5 - Western European and other 
```{r}
library(tidyverse)
library(ggplot2)
library(readxl)


corrdata <- read_excel("~/Downloads/Corruptclean2 (1).xlsx")
corrdata

genderdata <- read_excel("GenDip_Dataset_1968-2021.xlsx")
genderdata

globaldata <- read.csv()



corrdata <- corrdata|>
  mutate(
    year = as.integer(year), 
      corrupt_perc = as.integer(corrupt_perc)
  )
corrdata
```


```{r}

```



```{r}
plot_q2 <- ggplot(data = corrdata,
                  mapping = aes(x = region,
                                y = corrupt_perc)) +
  geom_boxplot() +
  facet_wrap(~ region, nrow = 1) +
  labs(
    x = "Continent",
    y = "Average Corruption Percentage in Different Regions 2000-2015"
  )
plot_q2
```

```{r}
by_continent_plot <- ggplot(data = corrdata,
                  mapping = aes(x = year, y = corrupt_perc)) +
  geom_line(mapping = aes(group = country), color = "gray70") + 
  geom_smooth(method = "loess", se = FALSE, linewidth = 1.1, color = "blue") +
              labs(
                x = "Year",
                y = "Corruption Level",
                title = "Corruption in Different Regions 2000-2015"
              ) +
  facet_wrap(~ region, nrow = 1)
by_continent_plot
```



```{r}
by_continent_scatter <- corrdata |>
  ggplot(mapping = aes(x = year,
                     y = corrupt_perc,
                     color =`country`, digits = 2)) +
  geom_point(alpha = 0.8) +
  labs(x = "Region",
       y = "Level of Corruption in Regional Countries")

by_continent_scatter
```

As seen by the Corruption in Different Regions 2000-2015 graph, countries in Africa tend to have higher levels of perceived corruption, while Western European have the lowest levels followed by Eastern European, Latin American and Carribean, and then Asian and Pacific Island Countries. 





